\documentclass{article}


\usepackage{graphicx} % Required for inserting images
\usepackage{a4wide}   % Width
\usepackage{hyperref} % Hyper links
\usepackage{tabularx} % More Tables 
\usepackage{subcaption}


\graphicspath{{Images/}}

% Config Links
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}


% % Redefine \section to be centered and unnumbered
% \titleformat{\section}
%   {\normalfont\Large\bfseries\centering} % Format: Large, bold, centered
%   {\thesection } % No section numbering
%   {0pt} % No extra space before title
%   {} % No extra code before the title

% % Redefine \subsection to be centered and unnumbered
% \titleformat{\subsection}
%   {\normalfont\large\bfseries\centering} % Format: large, bold, centered
%   {} % No subsection numbering
%   {0pt} % No extra space before title
%   {} % No extra code before the title

\title{Internet \& Web Systems Week 7 Progress}
\author{by Matthew Harper }
\date{October 2024}

\begin{document}

\maketitle
\section{Progress}
The progress for this week was good but less than I would have hoped. Again, there are a great deal of outside time pressures I am dealing with at this time.
This cycle, I had hoped to implement all of the API functions and the middle layers for the database. I was also able to implement the other two collections
I need for this project. That is the Username to UID mapping collection, which I expanded to hold group and key information as I determined I needed to do that. 
I also implemented the userData collection which is the core database used to store all of the user's inputs to the site. That is, the userData collection will
hold the passwords the users chose to trust the site with. Outside of this, I implemented the userIDs to identify admin vs non-admin users, and added those checks
to most of the API endpoints. I also created the framework for the Vulnerability management layer which is partially implemented but needs to be connected to the
API and admin pages to be functional. I also implemented the encryption and decryption of user passwords that are entered into the database, this is a rough
implementation as it lacks robust error checking.

\section{Not Completed}
I wanted to explore enabling HTTPs, however that was delayed due to other classwork requiring a significant amount of time again. Although I was able to implement
part of the Vulnerability middle layer, I wanted to implement the API so I would be able to test its functionality, as now it currently does not accomplish much.
As for the encryption and decryption of user passwords that are stored, I wanted to have robust error handling as although this is going to be a vulnerable site
to some degree, we do not want it to crash unexpectedly. Finally I wanted to start implementing more thorough logging, this way I can start to tie that into vulnerabilities.
\end{document}
